Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-08-25 paper.tex
Comparing to Weigel2010 Fig 8

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}

\usepackage[authoryear,square]{natbib}
\pagestyle{fancy}
\fancyhead[R]{Veibell \thepage}
\fancyhead[L]{}

@@

\section{Data Preparation}

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid. $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.  In the dataset, measurements from GOES 7 had the longest time span of coverage.  An overview of the data is given in Figure~\ref{AllData}.

% How does GOES 7 only effect result.

In this work events defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for 1987 to 1991, and not just pre-noon events}
\label{DailyAverages}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50~nT$ onset. (b) Same as (a) except around time intervals where mass density crossed above $40~amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50~nT$ for at least 12~hours. (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50~amu/cm^3$ for at least 12 hours.}
\label{Mspec}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80nT$ (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
\label{Dspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
\label{rhochange}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
\includegraphics[scale=0.5]{paperfigures/f107removed.eps}
\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
\label{nof107}
\end{figure}
\clearpage

\begin{figure}[htp]
\centering
\includegraphics[scale=0.75]{paperfigures/blockmedian.eps}
\includegraphics[scale=0.75]{paperfigures/blockmedian-prenoon.eps}
\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events. (b) Same, but only events starting between 0-12 UTC}
\label{blockmedian}
\end{figure}
\clearpage

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
\usepackage[authoryear,square]{natbib}
\pagestyle{fancy}
\fancyhead[R]{Veibell \thepage}
\fancyhead[L]{}

@@

\section{Data Preparation}
The parameters $\rho_{eq}$ used in this work is from the dataset associated with \cite{Denton}, with data available from 1980-1991 on a non-uniform 10 minute grid. The $F_{10.7}$ parameter comes from the OMNIWeb data collection at \cite{OMNIWeb} and covers 1980-2000 on an hourly grid, but with one daily value repeated for each hour of the day. All other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid. $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 6 was selected to avoid overlapping data points.  In the dataset, measurements from GOES 6 had the longest time span of coverage.  An overview of the data is given in Figure~\ref{AllData}.

In this work events are defined to occur when $D_{st}$ or $\rho_{eq}$ crosses a threshold value, as indicated in by horizontal dashed lines in the respective panels of Figure~\ref{AllData}.  In finding events, all fill values were replaced with linearly interpolated values.  Figure \ref{AllData} shows the values of $B_z$, $V_{SW}$, $D_{st}$, $F_{10.7}$, and Mass Density for the duration of the dataset.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-50-tak.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass-tak.eps}
\caption{(a) Verifying \cite{Takahashi2010} Fig. 11 conditions: $D_{st}<-50nT$ between 1989 and 1991 and (b) Same as (a) but for $\rho_{eq}$ events}
\label{DailyAverages}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-day.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass-day.eps}
\caption{Daily averages for all events in full time range for (a) $D_{st}<-50~nT$ events and (b) $\rho_{eq}>40~amu/cm^3$ events}
\label{DailyAveragesAllData}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below $-50~nT$ onset. (b) Same as (a) except around time intervals where mass density crossed above $40~amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ stayed below $-50~nT$ for at least 12~hours. (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ stayed above $50~amu/cm^3$ for at least 12 hours.}
\label{Mspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80nT$ (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
\label{Dspec}
\end{figure}

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-10amu.eps}
\rule[1ex]{5cm}{0.5pt}
\includegraphics[scale=0.45]{paperfigures/stormavs-diffden-30percent.eps}
\caption{(a) diff($\rho_{eq}$) $>$ 10$\frac{amu}{hour}$. (b) diff($\rho_{eq}$) $>$ 30$\frac{\%}{hour}$}
\label{rhochange}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst-nof107.eps}
\includegraphics[scale=0.45]{paperfigures/f107removed.eps}
\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
\label{nof107}
\end{figure}

\begin{figure}[htp]
\centering
\includegraphics[scale=0.45]{paperfigures/blockmedian.eps}
\includegraphics[scale=0.45]{paperfigures/blockmedian-prenoon.eps}
\caption{Comparing median values calculated as median of all 1-hour points in the 12 day block, and as the daily median of all hourly-mediated events. (b) Same, but only events starting between 0-12 UTC}
\label{blockmedian}
\end{figure}
\clearpage
